---
title: "MostImportantGenes"
format: html
editor: visual
---

## Loading packages - Setting options

```{r}
#library(renv)
#renv::init()
#install.packages("readxl")
library("readxl")
library(dplyr)
library(tidyr)
library(here)
library(snakecase)
library(ggplot2)
library(stringr)
library(writexl)
#renv::install("table1")
library(table1)
#renv::install("flextable")
#renv::install("officer")
library(flextable)
library(plotly)
#install.packages("targets")
#library(targets)
#use_targets()
set.seed(42069)
#renv::install("DescTools")
library(DescTools)

library(officer)
library(LMMstar)
library(multcomp)
library(butils)

#install.packages("corrplot")
library(corrplot)

library(ggplot2)
library("pheatmap")

library("plotly")

#set_here(path="C:/Users/mada0011/Desktop/Offline Statistics/Lupex-Statistics")
```

## Choose mITT, PP or ITT (by leaving both F)

```{r}
mITT = T
PP = F #I haven't made the PP analysis, and frankly I don't think I should, would the results be interpreted differently??

#IF you have full access to the data set this to true, if you do not have full access and this is not set to false, the code will not work
fullaccess = T

```

## Importing the data

```{r}
nanostring_biox<-
  read_excel(path=here("output","nanostring_ID_as_rows.xlsx"))

vo2max.data<-
  read_excel(path = here("Data","vo2max.xlsx"))

questionnaires.data<-
  read_excel(path = here("Output","Questionnaires_combined.xlsx"))

cytokine_score_sets<-
  readRDS(file = here("Input","Cytokine_score_sets.rds"))


Z_scores_nano<-read_excel(path=here("output","Z_scores_nanostring_ID_as_rows.xlsx"))
```

##Cluster analysis of IFN reduced lists:

```{r}
colnames(Z_scores_nano)<-
  colnames(Z_scores_nano)|>
  to_snake_case()

data.cluster_IFN_all_netto<-
  Z_scores_nano |>
  dplyr::filter(timepoint == "Baseline")|>
  dplyr::select(cytokine_score_sets$all_IFN_Netto)|>
  scale(scale = T, center = T)

clusters<-
  hclust(
  dist(data.cluster_IFN_all_netto, method = "euclidean"))

plot(clusters)

correlation.matrix.IFN.genes<-
  cor(data.cluster_IFN_all_netto, method = "pearson")

euclid.square.dist.cor.matr.square<-
  dist(correlation.matrix.IFN.genes, method = "euclidean")^2

correlation.cluster.IFN.Genes<-
  hclust(as.dist(1-correlation.matrix.IFN.genes), method = "average")

correlation.cluster.IFN.Genes|>plot()


correlation.plot.IFN.Genes<-
  corrplot(cor(data.cluster_IFN_all_netto))

correlation.plot.IFN.Genes

heatmap(cor(data.cluster_IFN_all_netto, method = "pearson"), scale = "row")

##HeatMap
dist.cor.cluster<-as.dist(1-correlation.matrix.IFN.genes)

plot_ly(x=colnames(data.cluster_IFN_all_netto),
        y=rownames(data.cluster_IFN_all_netto),
        z = data.cluster_IFN_all_netto,
        type = "heatmap")

#install.packages("pheatmap")

pretty_heat_IFN<-
  pheatmap(mat=correlation.matrix.IFN.genes, 
           cutree_rows = 14, cutree_cols=14,
           scale = "none",
           clustering_method = "average",
           cluster_rows = T,
           cluster_cols = T,
           clustering_distance_rows = "correlation",
           clustering_distance_cols = "correlation",
           display_numbers=F,
           number_format="%.1f",
           fontsize_number=5)

pretty_heat_IFN_kmeans4<-
  pheatmap(mat=correlation.matrix.IFN.genes, 
           kmeans_k = 6,
           #cutree_rows = 14, cutree_cols=14,
           scale = "none",
           clustering_method = "average",
           cluster_rows = T,
           cluster_cols = T,
           clustering_distance_rows = "correlation",
           clustering_distance_cols = "correlation",
           display_numbers=F,
           number_format="%.1f",
           fontsize_number=5)

#pretty_heat_IFN_single<-
#  pheatmap(mat=correlation.matrix.IFN.genes, 
#           cutree_rows = 12, cutree_cols=12,
#           scale = "none",
#           clustering_method = "single",
#           cluster_rows = T,
#           cluster_cols = T,
#           clustering_distance_rows = "correlation",
#           clustering_distance_cols = "correlation")

ggsave( filename = here("Output", "graphics","Pretty_Heat_IFN_Netto.JPG"), 
        plot = pretty_heat_IFN,
        width = 36,
        height = 36,
        units = "cm")

data.cluster<-
  Z_scores_nano |>
  dplyr::filter(timepoint == "Baseline")|>
  dplyr::select(where(is.numeric))|>
  dplyr::select(-c( "box_number", "sample_number"#,"mRNA.content.normalization.flag"
                    ))
correlation.matrix<-cor(data.cluster, method = "pearson")
euclid.dist.full.genes<-dist(correlation.matrix, method = "euclidean")

#pretty_heat<-pheatmap(correlation.matrix, cutree_rows = 12, cutree_cols=12, 
 #          clustering_method = "average")


```

## Cluster analysis of all genes

```{r}
time0<-Sys.time()
All_gene_Z_scores<-
  Z_scores_nano|>
  dplyr::filter(timepoint=="Baseline")|>
  dplyr::select(12:823)



correlation.matrix.ALL.genes<-
  cor(All_gene_Z_scores, method = "pearson")

euclid.dist.square.correlation.matrix.ALL.genes<-
  dist(correlation.matrix.ALL.genes)^2

hclust.cor.all.genes<-
  hclust(euclid.dist.square.correlation.matrix.ALL.genes, method="average")

plot(hclust.cor.all.genes)

#pretty_heat_ALL<-
 # pheatmap(mat=correlation.matrix.ALL.genes, 
  #         cutree_rows = 20, cutree_cols=20,
   #        scale = "none",
    #       clustering_method = "average",
     #      cluster_rows = T,
      #     cluster_cols = T,
       #    clustering_distance_rows = "correlation",
        #   clustering_distance_cols = "correlation",
         #  display_numbers=F,
          # number_format="%.1f",
           #fontsize_number=5)

time1<-Sys.time()
```

## Check most differently expressed genes

```{r}
nanostring_mergable <- 
  nanostring_biox|>
  dplyr::select(-c("BX_ID", "BXP ID" ,
                   "Box number",
                   "Sample number",
                   "Customer Sample ID",
                   "Sample type",
                   "Sample concentration (ng/µl)",
                   "Additional information",
                   "Sample check at BioXpedia (date/Init)",
                   "Samples returned /destroyed from BioXpedia (date/Init)",
                   "Maltes kommentar:",
                   "mRNA.content.normalization.flag"))|>
  dplyr::filter(
    timepoint == "Baseline" | timepoint == "HealthyControl"
  )|>mutate(
    group = factor(case_when(timepoint == "Baseline" ~ "Lupus",
                             T~ timepoint), 
                   levels = c("HealthyControl", "Lupus"))
  )

colnames(nanostring_mergable) <- 
  to_snake_case(colnames(nanostring_mergable))

genes<-colnames(nanostring_mergable)[1:826]
log2_diff <- rep(NA_real_, 826)
log2_SE <- rep(NA_real_, 826)
p_value <- rep(NA_real_, 826)
differentialExpressedGenes <- data.frame(
  genes , log2_diff ,log2_SE, p_value
)

linear.model<-lm(formula = reformulate( "group" ,response = gene),
             data = nanostring_mergable)

summary(linear.model)
for ( gene in genes){ # Do with Gene expression from 

    linear.model<-lm(formula = reformulate( "group" ,response = gene),
             data = nanostring_mergable)

    differentialExpressedGenes$p_value[gene == differentialExpressedGenes$genes] <- 
      summary(linear.model)$coefficients[8]
    differentialExpressedGenes$log2_SE[gene == differentialExpressedGenes$genes] <- 
      summary(linear.model)$coefficients[4]
    differentialExpressedGenes$log2_diff[gene == differentialExpressedGenes$genes] <- 
      summary(linear.model)$coefficients[2]
}
cut_off <- 0.05

differentialExpressedGenes <- 
  differentialExpressedGenes|>
  mutate(p_adjust = p.adjust(p_value, method = "fdr"),
         log_10_p = log(p_value,10),
         log_10_p_adjust= log(p_adjust,10),
         significance = case_when(p_value < cut_off ~ T,
                                  T ~ F),
         significance_adjust = case_when(p_adjust < cut_off ~ T,
                                  T ~ F))

log2_volcano_plot<- differentialExpressedGenes%>%
  ggplot(aes(
  x=log2_diff, 
  y=-log_10_p,
  color = significance,
  label = genes))+
  geom_point()+
  scale_color_manual(values = c("red","black"))+
  geom_hline(yintercept=-log(cut_off,10), linetype="dashed", color = "red")+
  theme(legend.position="none")

log2_volcano_plot
ggplotly(log2_volcano_plot)

log2_volcano_plot_FDRCORRECTED<- 
  differentialExpressedGenes%>%
  ggplot(aes(
  x=log2_diff, 
  y=-log_10_p_adjust,
  color = significance_adjust,
  label = genes))+
  geom_point()+
  scale_color_manual(values = c("red","black"))+
  geom_hline(yintercept=-log(cut_off,10), linetype="dashed", color = "red")+
  theme(legend.position="none")

log2_volcano_plot_FDRCORRECTED
ggplotly(log2_volcano_plot_FDRCORRECTED)
```

## Loop that finds effect of each gene in a Linear Mixed Model. With GLHT of the effect.

This is a fishing expedition, but we'll call it hypothesis generating so it's all going to be fine.

So Let's go fishing I guess

### Combined data set with all primary, secondary and transcriptomics. Transcriptomics at baseline at both BL and FU.

```{r}
data_vo2max_QC<-read_excel(
  path = here("Output","VO2maxQC","Data.VO2MAXQC.xlsx")
)

data_vo2max_QC<-
  data_vo2max_QC|>
  dplyr::select(id, timepoint, aerobiccapacity, aerobiccapacity_noted, QualityMeasurementCS, easytrialQualityTest, QualityMeasurementMLA, operator)

vo2_with_quality_controls<-vo2max.data|>left_join(data_vo2max_QC)|>
  mutate(timepoint = factor(timepoint, levels = c("screening", "baseline", "followup")))

vo2max.combined.data<-
  vo2_with_quality_controls|>
  dplyr::select(id, timepoint, treatment, treat, sex,
                aerobiccapacity, vo_2_max, kondital, easytrialQualityTest)

questionnaires.combined.data<-
  questionnaires.data|>
  dplyr::select(id, timepoint, treatment, treat, 
                fatigue.mean, physical.component.score, mental.component.score)|>
  rename( SF36.Physical = physical.component.score,
          SF36.Mental = mental.component.score)

SLEDAI.combined.data<-
  read_excel(path = here("Data",paste0("SLEDAI.data.xlsx")))|>
  dplyr::select(id, treatment, timepoint, SLEDAI_score, vas_sledai_physician)

nanostring.combined.data<-
  nanostring_mergable|>
  mutate(id = to_snake_case(id))|>
  dplyr::filter(timepoint == "Baseline")|>
  dplyr::select(-c(timepoint, group))

combined.data<-
  vo2max.combined.data|>
  left_join(questionnaires.combined.data)|>
  left_join(SLEDAI.combined.data)|>
  left_join(nanostring.combined.data)


```

### Loop over genes, find effect, put into table.

```{r warning=FALSE message=F eval = F}
differentialExpressedGenes<-
  differentialExpressedGenes|>
  mutate(
    effect_VO2max = NA_real_,
    p_value_VO2max = NA_real_,
    effect_fatigue = NA_real_,
    p_value_fatigue = NA_real_,
    
  )

cont_vec_vo2 <-
  rbind(
    c(   #Difference of M_1_2 interaction
      0, #(Intercept)
      0, #timepointfollowup
      0, #timepointscreening	
      0, #sexM	
      0, #gene	
      0, #timepointfollowup:treatexercise
     -1, #timepointfollowup:treatcontrol:gene
      0, #timepointscreening:treatcontrol:gene	
      1  #timepointfollowup:treatexercise:gene
    ))

rownames(cont_vec_vo2) <- c("Difference gene effect exercise minus control")

 time1 <- Sys.time()
for (gene in differentialExpressedGenes$genes){
  lmm<-lmm(formula = 
            reformulate(c("timepoint","treat","sex",gene,"treat:timepoint", paste0(gene,":timepoint+","treat:timepoint:",gene)) ,
                        response = "aerobiccapacity"),
           repetition = ~timepoint|id,
           structure = "UN",
              data = combined.data)
  tb <- 
  lmm|>
  glht(linfct=cont_vec_vo2)|>
  butils::multcomp2table(
  method.glht = "glht", 
  conf.level = 0.95, 
  digits.p.value = 7, 
  method.multcomp="none")

differentialExpressedGenes$p_value_VO2max[gene == differentialExpressedGenes$genes] <- 
  as.numeric(tb$p.value[1])
differentialExpressedGenes$effect_VO2max[gene == differentialExpressedGenes$genes] <-
  as.numeric(tb$Estimate[1])

}
  time2 <- Sys.time()
  time2-time1
 
# gene <- "jak_3"

# lmm<-lmm(formula = 
#            reformulate(c("timepoint","treat","sex",gene,"treat:timepoint", paste0("treat:timepoint:",gene)) ,
#                        response = "fatigue.mean"),
#           repetition = ~timepoint|id,
#           structure = "UN",
#              data = combined.data)
# plot(lmm, type = "scatterplot")
#summary(lmm)

cont_vec <-
  rbind(
    c(   #Difference of M_1_2 interaction
      0, #(Intercept)
      0, #timepointfollowup
      0, #sexM
      0, #gene	
      0, #timepointfollowup:treatexercise
     -1, #timepointfollowup:treatcontrol:gene
      1  #timepointfollowup:treatexercise:gene
    ))

rownames(cont_vec) <- c("Difference gene effect exercise minus control")

time3 <- Sys.time()
 
 for (gene in genes){
  lmm<-lmm(formula = 
            reformulate(c("timepoint","treat","sex",gene,"treat:timepoint", paste0("treat:timepoint:",gene)) ,
                        response = "fatigue.mean"),
           repetition = ~timepoint|id,
           structure = "UN",
              data = combined.data)
tb <- 
  lmm|>
  glht(linfct=cont_vec)|>
  butils::multcomp2table(
  method.glht = "glht", 
  conf.level = 0.95, 
  digits.p.value = 7,
  method.multcomp="none")

differentialExpressedGenes$p_value_fatigue[gene == differentialExpressedGenes$genes] <- 
  as.numeric(tb$p.value[1])
differentialExpressedGenes$effect_fatigue[gene == differentialExpressedGenes$genes] <- 
  as.numeric(tb$Estimate[1])

 }
time4<-Sys.time()
time4-time3
 
 differentialExpressedGenes<-
   differentialExpressedGenes|>
   mutate(p_adjust_VO2max =p.adjust(p_value_VO2max, method = "fdr"),
          p_adjust_fatigue =p.adjust(p_value_fatigue, method = "fdr"))|>
   arrange(genes)
 
 differentialExpressedGenes|>
   saveRDS(
   file = 
     here( "Output","DifferentialExpression","Genes effect on fatigue and vo2max as well as expression differences between HC and SLE.rds")
 )
 
 differentialExpressedGenes|>
   write_xlsx(
   path = 
     here( "Output","DifferentialExpression","Genes effect on fatigue and vo2max as well as expression differences between HC and SLE.xlsx")
 )
 
```

### Loop for secondary outcomes??

No
