---
title: "PETStudy"
format: html
editor: visual
---

## PET-STUDY

This this the study were we focus on the 82-Rb-Rest/Stress PET-CTs and the other pulmonary outcomes.

```{r}
library(renv)
#renv::init()
#install.packages("readxl")
library("readxl")
library(dplyr)
library(tidyr)
library(here)
library(snakecase)
library(ggplot2)
library(stringr)
library(writexl)
#renv::install("table1")
library(table1)
#renv::install("flextable")
#renv::install("officer")
library(flextable)
#install.packages("targets")
#library(targets)
#use_targets()
set.seed(42069)
#renv::install("DescTools")
library(DescTools)
library(lubridate)

library(officer)

#set_here(path="C:/Users/mada0011/Desktop/Offline Statistics/Lupex-Statistics")
here::i_am("Code/PETStudy.qmd")
```

So here's the outline of the plan: We'll load the Pet-CT data, the pulmonary tests and the table 1 data we already have, we'll then check whether it'll be easier to implement the table 1 data into the workflow in the datawrangling.qmd or whether we'll just do it here.

Then first the descriptive statistics, then the raw change scores, then we'll do the models on outcomes, and add that together to form table 2 and 3. Then we'll do figures and voila we have our project done.

## Load data

```{r}
pet_data <-
  read_excel(here("Data","PET-CT","PBV_LUPEX.xlsx"))%>%
  mutate(
    id = to_snake_case(ID),
    timepoint = Timepoint,
  )%>%
  relocate(
    id, timepoint
  )

lfu_data<-
  read_excel(here("Data/easy_trial_seperate_schemes/_d_visit__lfu.data .xlsx"))%>%
  mutate(
    Timepoint = 
      case_when(
        grepl(
          "aseline", task_name
        ) ~ "Baseline",
        grepl(
          "ollow", task_name
        ) ~ "Followup",
        T~NA_character_
      )
  ) %>% mutate(fev_1_fvc_rå = round(100*fev_1 / fvc_rå,2)) #Recalculate ratio in case someone put it in incorrectly as for LUP007 followup.

vO2_data<-
  read_excel(path = here("Output","VO2maxQC","Data.VO2MAXQC.xlsx"))%>%
  mutate(
    Timepoint = factor(
      timepoint, levels = c("screening", "baseline", "followup"), labels = c("Screening", "Baseline", "Followup")))%>%
  dplyr::select(
        id, Timepoint, aerobiccapacity, 
        borg, HRmax, maxRQ, 
        vslope_vent_threshold, O2_vent_thresh, CO2_vent_tresh
      )

other_data <- 
  read_excel(here("data","data.table1.xlsx"))%>%
  dplyr::select(id, 
                timepoint,
                age,
                pack_years, smoking_status, waist_height_ratio,
                sle_start_dato,  SLEDAI_score, slicc_score,
                FSS, aerobic_capacity, vo_2_max, duration_daily_MVPA_pla,
                Energy_kJ_mean, total_fat_percentage)%>%
  mutate(
    Timepoint = factor(
      timepoint, levels = c("screening", "baseline", "followup"), labels = c("Screening", "Baseline", "Followup"))
  )%>%
  group_by(id)%>%
  mutate(pack_years =
           case_when(
             smoking_status == "Never Smoker" ~ 0,
             T ~ pack_years
           ))%>%
  fill(age,
       pack_years,
       smoking_status,
       waist_height_ratio,
       age,
       sle_start_dato,
       .direction = "updown")

pet_lung_data<-
 vO2_data%>%
  left_join(pet_data, join_by(id, Timepoint))%>%
  left_join(other_data, join_by(id, Timepoint))%>%
  left_join(lfu_data, join_by(id, Timepoint))%>%
  mutate(
    Timepoint = factor(Timepoint, levels = c("Screening","Baseline","Followup")),
    sex = factor(sex, labels = c("Female","Male"), levels = c("F","M")),
    SLE_duration_months = as.numeric(task_start - sle_start_dato) / 30.44,
    HR_R_LM=`HR_R_(LM)`,
    HR_S_LM=`HR_S_(LM)`,
    S_R_ratio_PBV = `S/R ratio PBV`
  )%>%
  group_by(id)%>%
  fill(sex, .direction = "up")%>%
  relocate(
    id, Timepoint, sex
  )%>%
  dplyr::select(!(
    participant_id: schema_version_id
  )
  ) 
```

## Table 1

using table1 package, we'll import some stuff from tablesRus.qmd and make it here 
### Data Set

```{r}
#list_normal_dist <- list()

#rndr <- function(x, name, ...) {
#    if (!is.numeric(x)) return(render.categorical.default(x))
#  what <-
#    case_when(
#   name %in% list_normal_dist ~ c(.="N", .="Mean (SD)", .="NMISS"),
#   T ~ c(.="N",  .="Median [Q1, Q3]", .="NMISS"))
#    parse.abbrev.render.code(c(what))(x)
#}

pet_lung_table_1.data <-
  pet_lung_data %>%
  dplyr::filter(Timepoint == "Baseline")%>%
  dplyr::filter(
    !is.na(Scanningsdato)
  )%>%mutate(
    treatment = str_to_title(treatment)
  )
```

### Labels and Units

```{r}
label(pet_lung_table_1.data$sex) <- "Sex"
label(pet_lung_table_1.data$age) <- "Age"
label(pet_lung_table_1.data$Weight) <- "Weight"
label(pet_lung_table_1.data$Height) <- "Height"
label(pet_lung_table_1.data$BMI) <- "BMI"
label(pet_lung_table_1.data$borg) <- "RPE"
label(pet_lung_table_1.data$Body_Surface_DuBois) <- "Body Surface (DuBois)"
label(pet_lung_table_1.data$smoking_status) <- "Smoking Status"
label(pet_lung_table_1.data$pack_years) <- "Pack Years"
label(pet_lung_table_1.data$fev_1) <- "FEV 1"
label(pet_lung_table_1.data$fev_1_pred) <- "FEV 1 percent of predicted"
label(pet_lung_table_1.data$fvc_rå) <- "FVC"
label(pet_lung_table_1.data$fvc_pred) <- "FVC percent of predicted"
label(pet_lung_table_1.data$fev_1_fvc_rå) <- "FEV 1 / FVC ratio"
label(pet_lung_table_1.data$fev_fvc_pred) <- "FEV 1 / FVC ratio percent of predicted"
label(pet_lung_table_1.data$tlv_rå) <- "TLV"
label(pet_lung_table_1.data$tlv_pred) <- "TLV percent of predicted"
label(pet_lung_table_1.data$rv_rå) <- "RV"
label(pet_lung_table_1.data$rv_pred) <- "RV percent of predicted"
label(pet_lung_table_1.data$dlc_oc_rå) <- "DLCO"
label(pet_lung_table_1.data$dlc_oc_pred) <- "DLCO percent of predicted"
label(pet_lung_table_1.data$va_rå) <- "VA"
label(pet_lung_table_1.data$va_pred) <- "VA percent of predicted"
label(pet_lung_table_1.data$kco_rå) <- "KCO"
label(pet_lung_table_1.data$kco_pred) <- "KCO percent of predicted"
label(pet_lung_table_1.data$HR_R_LM) <- "82Rb PET-CT - Heart Rate - Rest"
label(pet_lung_table_1.data$HR_S_LM) <- "82Rb PET-CT - Heart Rate - Stress"
label(pet_lung_table_1.data$MTT_Rest) <- "MTT Rest"
label(pet_lung_table_1.data$MTT_Stress) <- "MTT Stress"
label(pet_lung_table_1.data$EDV_R) <- "EDV - Rest"
label(pet_lung_table_1.data$ESV_R) <- "ESV - Rest"
label(pet_lung_table_1.data$SV_R) <- "Stroke Volume - Rest"
label(pet_lung_table_1.data$LVEF_R) <- "LVEF - Rest"
label(pet_lung_table_1.data$EDV_S) <- "EDV - Stress"
label(pet_lung_table_1.data$ESV_S) <- "ESV - Stress"
label(pet_lung_table_1.data$SV_S) <- "Stroke Volume - Stress"
label(pet_lung_table_1.data$LVEF_S) <- "LVEF - Stress"
label(pet_lung_table_1.data$LVEF_Reser) <- "LVEF - Reserve"
label(pet_lung_table_1.data$PBV_R) <- "PBV - Rest"
label(pet_lung_table_1.data$PBS_S) <- "PBV - Stress"
label(pet_lung_table_1.data$S_R_ratio_PBV) <- "PBV - Stress / Rest Ratio"
label(pet_lung_table_1.data$SLE_duration_months) <- "SLE Duration"
label(pet_lung_table_1.data$SLEDAI_score) <- "SLEDAI"
label(pet_lung_table_1.data$slicc_score) <- "SLICC"
label(pet_lung_table_1.data$FSS) <- "FSS"
label(pet_lung_table_1.data$aerobic_capacity) <- "Aerobic Capacity"
label(pet_lung_table_1.data$vo_2_max) <- "VO2max"
label(pet_lung_table_1.data$O2_vent_thresh) <- "O2 Ventilatory Threshold"
label(pet_lung_table_1.data$CO2_vent_tresh) <- "CO2 Ventilatory Threshold"
label(pet_lung_table_1.data$vslope_vent_threshold) <- 
  "Ventilatory Threshold percentage of VO2max"
label(pet_lung_table_1.data$duration_daily_MVPA_pla)<- "Daily MVPA"
label(pet_lung_table_1.data$Energy_kJ_mean) <- "Daily KJ intake"
label(pet_lung_table_1.data$all_ifn_netto_t_test) <- "All IFN Score"
label(pet_lung_table_1.data$ifn_1_netto) <- "IFN-1 score"


units(pet_lung_table_1.data$Weight) <- "Kg"
units(pet_lung_table_1.data$Height) <- "cm"
units(pet_lung_table_1.data$BMI) <- "Kg/m^2"
units(pet_lung_table_1.data$borg) <- "borg"
units(pet_lung_table_1.data$Body_Surface_DuBois) <- "m^2"
units(pet_lung_table_1.data$pack_years) <- "Years"
units(pet_lung_table_1.data$fev_1) <- "L"
units(pet_lung_table_1.data$fev_1_pred) <- "%"
units(pet_lung_table_1.data$fvc_rå) <- "L"
units(pet_lung_table_1.data$fvc_pred) <- "%"
units(pet_lung_table_1.data$fev_1_fvc_rå) <- "%"
units(pet_lung_table_1.data$fev_fvc_pred) <- "%"
units(pet_lung_table_1.data$tlv_rå) <- "L"
units(pet_lung_table_1.data$tlv_pred) <- "%"
units(pet_lung_table_1.data$rv_rå) <- "L"
units(pet_lung_table_1.data$rv_pred) <- "%"
units(pet_lung_table_1.data$dlc_oc_rå) <- "ml/min/kPa"
units(pet_lung_table_1.data$dlc_oc_pred) <- "%"
units(pet_lung_table_1.data$va_rå) <- "L/min"
units(pet_lung_table_1.data$va_pred) <- "%"
units(pet_lung_table_1.data$kco_rå) <- "mmol/min/kPa/L"
units(pet_lung_table_1.data$kco_pred) <- "%"
units(pet_lung_table_1.data$HR_R_LM) <- "bpm"
units(pet_lung_table_1.data$HR_S_LM) <- "bpm"
units(pet_lung_table_1.data$MTT_Rest) <- "s"
units(pet_lung_table_1.data$MTT_Stress) <- "s"
units(pet_lung_table_1.data$EDV_R) <- "ml"
units(pet_lung_table_1.data$ESV_R) <- "ml"
units(pet_lung_table_1.data$SV_R) <- "ml"
units(pet_lung_table_1.data$LVEF_R) <- "%"
units(pet_lung_table_1.data$EDV_S) <- "ml"
units(pet_lung_table_1.data$ESV_S) <- "ml"
units(pet_lung_table_1.data$SV_S) <- "ml"
units(pet_lung_table_1.data$LVEF_S) <- "%"
units(pet_lung_table_1.data$LVEF_Reser) <- "%"
units(pet_lung_table_1.data$PBV_R) <- "ml"
units(pet_lung_table_1.data$PBS_S) <- "ml"
#units(pet_lung_table_1.data$S_R_ratio_PBV) <- "PBV - Stress / Rest Ratio"
units(pet_lung_table_1.data$SLE_duration_months) <- "Months"
#units(pet_lung_table_1.data$SLEDAI_score) <- "SLEDAI"
#units(pet_lung_table_1.data$slicc_score) <- "SLICC"
#units(pet_lung_table_1.data$FSS) <- "FSS"
units(pet_lung_table_1.data$aerobic_capacity) <- "ml/min/kg"
units(pet_lung_table_1.data$vo_2_max) <- "ml/min"
units(pet_lung_table_1.data$O2_vent_thresh) <- "ml/min"
units(pet_lung_table_1.data$CO2_vent_tresh) <- "ml/min"
units(pet_lung_table_1.data$vslope_vent_threshold) <- "%"
units(pet_lung_table_1.data$duration_daily_MVPA_pla)<- "Minutes"
units(pet_lung_table_1.data$Energy_kJ_mean) <- "KJ"
units(pet_lung_table_1.data$all_ifn_netto_t_test) <- "Z-score"
units(pet_lung_table_1.data$ifn_1_netto) <- "Z-score"
```

### Normal distributions,

The Render function prefers to know whether we have a normal distribution or not, so lets take a look at histograms and consider based on this.

```{r}
check_dist <- list(
  "age",              "Weight",
              "Height",
              "BMI",
              "borg",
              "Body_Surface_DuBois",
              #"smoking_status",
              "pack_years",
              "fev_1",
              "fev_1_pred",
              "fev_1_fvc_rå",
              "fev_fvc_pred",
              "tlv_rå",
              "tlv_pred",
              "rv_rå",
              "rv_pred",
              "dlc_oc_rå",
              "dlc_oc_pred",
              "va_rå",
              "va_pred",
              "kco_rå",
              "kco_pred",
              "HR_R_(LM)",
              "HR_S_(LM)",
              "MTT_Rest",
              "MTT_Stress",
              "EDV_R","ESV_R","SV_R","LVEF_R",
              "EDV_S","ESV_S","SV_S","LVEF_S",
              "LVEF_Reser",
              "PBV_R","PBS_S",
              "S/R ratio PBV",     
           #TODO Add lung parameters and PET parameters
              #weekly_exercise_sessions_baseline +
              #exercise_intensity_baseline +
              #exercise_duration_baseline +
              "SLE_duration_months",
              "SLEDAI_score",
              "slicc_score",
              "FSS",
              "aerobic_capacity",
              "vo_2_max",
              "O2_vent_thresh",
              "CO2_vent_tresh",
              "vslope_vent_threshold",
              "duration_daily_MVPA_pla",
              "Energy_kJ_mean",
              "total_fat_percentage",
              
              #prednisolone_baseline+
              #plaquenil_baseline+
              #methotrexate_baseline+
              #mycophenolate_baseline+
              #ciclosporine_baseline+
              #azathioprine_baseline+
              #hemoglobin+
              #thrombocytes+
              #beta2_microglobuline+
              "all_ifn_netto_t_test",
              "ifn_1_netto")

histograms<-list()    
for(var in check_dist){
  histograms[var]<-pet_lung_table_1.data%>%
  ggplot(
  aes(x = .data[[as.character(var)]]))+
  geom_histogram()
  
  
  
} 
histograms

```

####Assign Normal Distributions From the histograms we assign outcomes that follow a normal distribution, and those that do not

```{r}


norm_dist <- list(
  "age","Weight",
              "Height",
              "BMI",
              "borg",
              "Body_Surface_DuBois",
              #"smoking_status",
              #"pack_years",
              "fev_1",
              "fev_1_pred",
              "fev_1_fvc_rå",
              "fev_fvc_pred",
              #"tlv_rå",
              "tlv_pred",
              "rv_rå",
              "rv_pred",
              "dlc_oc_rå",
              "dlc_oc_pred",
              "va_rå",
              "va_pred",
              "kco_rå",
             # "kco_pred",
              #"HR_R_(LM)",
              #"HR_S_(LM)",
              "MTT_Rest",
              "MTT_Stress",
              "EDV_R","ESV_R","SV_R",#"LVEF_R",
              "EDV_S","ESV_S","SV_S",#"LVEF_S",
              #"LVEF_Reser",
              "PBV_R","PBS_S",
              "S/R ratio PBV",     
           #TODO Add lung parameters and PET parameters
              #weekly_exercise_sessions_baseline +
              #exercise_intensity_baseline +
              #exercise_duration_baseline +
              #"SLE_duration_months",
              #"SLEDAI_score",
              #"slicc_score",
              "FSS",
              "aerobic_capacity",
              "vo_2_max",
              "O2_vent_thresh",
              "CO2_vent_tresh",
              "vslope_vent_threshold",
              "duration_daily_MVPA_pla",
              "Energy_kJ_mean",
              "total_fat_percentage"
  #,
              
              #prednisolone_baseline+
              #plaquenil_baseline+
              #methotrexate_baseline+
              #mycophenolate_baseline+
              #ciclosporine_baseline+
              #azathioprine_baseline+
              #hemoglobin+
              #thrombocytes+
              #beta2_microglobuline+
              #"all_ifn_netto_t_test",
              #"ifn_1_netto",
  )

rndr <- function(x, name, ...) {
    if (!is.numeric(x)) return(render.categorical.default(x))
  what <-
    case_when(
   name %in% norm_dist ~ c(.="N", .="Mean (SD)", .="NMISS"),
   T ~ c(.="N",  .="Median [Q1, Q3]", .="NMISS"))
    parse.abbrev.render.code(c(what))(x)
}

```

### Create Table

```{r}
t1_pet_lung<-
  pet_lung_table_1.data%>%
  table1(x= ~ 
              sex +
              age +
              Weight+
              Height+
              BMI +
              borg+
              Body_Surface_DuBois+
              smoking_status+
              pack_years+
              fev_1+
              fev_1_pred +
              fev_1_fvc_rå +
              fev_fvc_pred+
              tlv_rå+
              tlv_pred+
              rv_rå+
              rv_pred+
              dlc_oc_rå+
              dlc_oc_pred+
              va_rå+
              va_pred+
              kco_rå+
              kco_pred+
              HR_R_LM+HR_S_LM+MTT_Rest+MTT_Stress+
              EDV_R+ESV_R+SV_R+LVEF_R+
              EDV_S+ESV_S+SV_S+LVEF_S+
              LVEF_Reser+
              PBV_R+PBS_S+
              S_R_ratio_PBV+     
           #TODO Add lung parameters and PET parameters
              #weekly_exercise_sessions_baseline +
              #exercise_intensity_baseline +
              #exercise_duration_baseline +
              SLE_duration_months+
              SLEDAI_score+
              slicc_score+
              FSS +
              aerobic_capacity +
              vo_2_max +
              O2_vent_thresh+
              CO2_vent_tresh+
              vslope_vent_threshold+
              duration_daily_MVPA_pla+
              Energy_kJ_mean+
              #total_fat_percentage+
              
              #prednisolone_baseline+
              #plaquenil_baseline+
              #methotrexate_baseline+
              #mycophenolate_baseline+
              #ciclosporine_baseline+
              #azathioprine_baseline+
              #hemoglobin+
              #thrombocytes+
              #beta2_microglobuline+
              all_ifn_netto_t_test+
              ifn_1_netto|
              treatment,
              render=rndr,
              #render.continuous = c(.="N", .="Mean (SD)", .="Median [Q1, Q3]"),
              #render.categorical = my.render.cat,
            #render.missing = T,
            data = .)
t1_pet_flex<-t1flex(t1_pet_lung)


t1_pet_flex
```


## Table 2

### Data Set
```{r}
#TODO
```


##Models Load LMMStar

```{r}
library(LMMstar)
pet_lung_data<-
  pet_lung_data %>%
  mutate(
    treat = 
      case_when(
        Timepoint =="Baseline" ~ "control",
        Timepoint =="Screening" ~ "control",
        T~treatment
      )
  )
```

###fev1

```{r}

model.fev_1<-
  lmm(
  formula = 
    fev_1 ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1)
plot(model.fev_1,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1, type = "scatterplot")
plot(model.fev_1, type = "scatterplot2")
plot(model.fev_1, type = "qqplot")



model.fev_1_interaction <-
  lmm(
  formula = 
    fev_1 ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1_interaction)
plot(model.fev_1_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1_interaction, type = "scatterplot")
plot(model.fev_1_interaction, type = "scatterplot2")
plot(model.fev_1_interaction, type = "qqplot")
```

###fev1_pred

```{r}

model.fev_1_pred<-
  lmm(
  formula = 
    fev_1_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1_pred)
plot(model.fev_1_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1_pred, type = "scatterplot")
plot(model.fev_1_pred, type = "scatterplot2")
plot(model.fev_1_pred, type = "qqplot")


model.fev_1_pred_interaction <-
  lmm(
  formula = 
    fev_1_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1_pred_interaction)
plot(model.fev_1_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1_pred_interaction, type = "scatterplot")
plot(model.fev_1_pred_interaction, type = "scatterplot2")
plot(model.fev_1_pred_interaction, type = "qqplot")
```

###fev_1_fvc_rå

```{r}

model.fev_1_fvc_rå<-
  lmm(
  formula = 
    fev_1_fvc_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1_fvc_rå)
plot(model.fev_1_fvc_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1_fvc_rå, type = "scatterplot")
plot(model.fev_1_fvc_rå, type = "scatterplot2")
plot(model.fev_1_fvc_rå, type = "qqplot")

model.fev_1_fvc_rå_interaction <-
  lmm(
  formula = 
    fev_1_fvc_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_1_fvc_rå_interaction)
plot(model.fev_1_fvc_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_1_fvc_rå_interaction, type = "scatterplot")
plot(model.fev_1_fvc_rå_interaction, type = "scatterplot2")
plot(model.fev_1_fvc_rå_interaction, type = "qqplot")
```

###fev_fvc_pred

```{r}

model.fev_fvc_pred<-
  lmm(
  formula = 
    fev_fvc_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_fvc_pred)
plot(model.fev_fvc_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_fvc_pred, type = "scatterplot")
plot(model.fev_fvc_pred, type = "scatterplot2")
plot(model.fev_fvc_pred, type = "qqplot")

model.fev_fvc_pred_interaction <-
  lmm(
  formula = 
    fev_fvc_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.fev_fvc_pred_interaction)
plot(model.fev_fvc_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.fev_fvc_pred_interaction, type = "scatterplot")
plot(model.fev_fvc_pred_interaction, type = "scatterplot2")
plot(model.fev_fvc_pred_interaction, type = "qqplot")
```

###tlv_rå

```{r}

model.tlv_rå<-
  lmm(
  formula = 
    tlv_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.tlv_rå)
plot(model.tlv_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.tlv_rå, type = "scatterplot")
plot(model.tlv_rå, type = "scatterplot2")
plot(model.tlv_rå, type = "qqplot")

model.tlv_rå_interaction <-
  lmm(
  formula = 
    tlv_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.tlv_rå_interaction)
plot(model.tlv_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.tlv_rå_interaction, type = "scatterplot")
plot(model.tlv_rå_interaction, type = "scatterplot2")
plot(model.tlv_rå_interaction, type = "qqplot")
```

###tlv_pred

```{r}

model.tlv_pred<-
  lmm(
  formula = 
    tlv_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.tlv_pred)
plot(model.tlv_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.tlv_pred, type = "scatterplot")
plot(model.tlv_pred, type = "scatterplot2")
plot(model.tlv_pred, type = "qqplot")

model.tlv_pred_interaction <-
  lmm(
  formula = 
    tlv_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.tlv_pred_interaction)
plot(model.tlv_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.tlv_pred_interaction, type = "scatterplot")
plot(model.tlv_pred_interaction, type = "scatterplot2")
plot(model.tlv_pred_interaction, type = "qqplot")
```

###rv_rå

```{r}

model.rv_rå<-
  lmm(
  formula = 
    rv_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.rv_rå)
plot(model.rv_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.rv_rå, type = "scatterplot")
plot(model.rv_rå, type = "scatterplot2")
plot(model.rv_rå, type = "qqplot")


model.rv_rå_interaction <-
  lmm(
  formula = 
    rv_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.rv_rå_interaction)
plot(model.rv_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.rv_rå_interaction, type = "scatterplot")
plot(model.rv_rå_interaction, type = "scatterplot2")
plot(model.rv_rå_interaction, type = "qqplot")
```

###rv_pred

```{r}

model.rv_pred<-
  lmm(
  formula = 
    rv_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.rv_pred)
plot(model.rv_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.rv_pred, type = "scatterplot")
plot(model.rv_pred, type = "scatterplot2")
plot(model.rv_pred, type = "qqplot")


model.rv_pred_interaction <-
  lmm(
  formula = 
    rv_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.rv_pred_interaction)
plot(model.rv_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.rv_pred_interaction, type = "scatterplot")
plot(model.rv_pred_interaction, type = "scatterplot2")
plot(model.rv_pred_interaction, type = "qqplot")
```

###dlc_oc_rå

```{r}

model.dlc_oc_rå<-
  lmm(
  formula = 
    dlc_oc_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.dlc_oc_rå)
plot(model.dlc_oc_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.dlc_oc_rå, type = "scatterplot")
plot(model.dlc_oc_rå, type = "scatterplot2")
plot(model.dlc_oc_rå, type = "qqplot")


model.dlc_oc_rå_interaction <-
  lmm(
  formula = 
    dlc_oc_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.dlc_oc_rå_interaction)
plot(model.dlc_oc_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.dlc_oc_rå_interaction, type = "scatterplot")
plot(model.dlc_oc_rå_interaction, type = "scatterplot2")
plot(model.dlc_oc_rå_interaction, type = "qqplot")
```

###dlc_oc_pred

```{r}

model.dlc_oc_pred<-
  lmm(
  formula = 
    dlc_oc_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.dlc_oc_pred)
plot(model.dlc_oc_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.dlc_oc_pred, type = "scatterplot")
plot(model.dlc_oc_pred, type = "scatterplot2")
plot(model.dlc_oc_pred, type = "qqplot")


model.dlc_oc_pred_interaction <-
  lmm(
  formula = 
    dlc_oc_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.dlc_oc_pred_interaction)
plot(model.dlc_oc_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.dlc_oc_pred_interaction, type = "scatterplot")
plot(model.dlc_oc_pred_interaction, type = "scatterplot2")
plot(model.dlc_oc_pred_interaction, type = "qqplot")
```

###va_rå

```{r}

model.va_rå<-
  lmm(
  formula = 
    va_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.va_rå)
plot(model.va_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.va_rå, type = "scatterplot")
plot(model.va_rå, type = "scatterplot2")
plot(model.va_rå, type = "qqplot")


model.va_rå_interaction <-
  lmm(
  formula = 
    va_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.va_rå_interaction)
plot(model.va_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.va_rå_interaction, type = "scatterplot")
plot(model.va_rå_interaction, type = "scatterplot2")
plot(model.va_rå_interaction, type = "qqplot")
```

###va_pred

```{r}

model.va_pred<-
  lmm(
  formula = 
    va_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.va_pred)
plot(model.va_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.va_pred, type = "scatterplot")
plot(model.va_pred, type = "scatterplot2")
plot(model.va_pred, type = "qqplot")

model.va_pred_interaction <-
  lmm(
  formula = 
    va_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.va_pred_interaction)
plot(model.va_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.va_pred_interaction, type = "scatterplot")
plot(model.va_pred_interaction, type = "scatterplot2")
plot(model.va_pred_interaction, type = "qqplot")
```

###kco_rå

```{r}

model.kco_rå<-
  lmm(
  formula = 
    kco_rå ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.kco_rå)
plot(model.kco_rå,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.kco_rå, type = "scatterplot")
plot(model.kco_rå, type = "scatterplot2")
plot(model.kco_rå, type = "qqplot")

model.kco_rå_interaction <-
  lmm(
  formula = 
    kco_rå ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.kco_rå_interaction)
plot(model.kco_rå_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.kco_rå_interaction, type = "scatterplot")
plot(model.kco_rå_interaction, type = "scatterplot2")
plot(model.kco_rå_interaction, type = "qqplot")
```

###kco_pred

```{r}

model.kco_pred<-
  lmm(
  formula = 
    kco_pred ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.kco_pred)
plot(model.kco_pred,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.kco_pred, type = "scatterplot")
plot(model.kco_pred, type = "scatterplot2")
plot(model.kco_pred, type = "qqplot")

model.kco_pred_interaction <-
  lmm(
  formula = 
    kco_pred ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.kco_pred_interaction)
plot(model.kco_pred_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.kco_pred_interaction, type = "scatterplot")
plot(model.kco_pred_interaction, type = "scatterplot2")
plot(model.kco_pred_interaction, type = "qqplot")
```

###HR_R_(LM)

```{r}

model.HR_R_LM<-
  lmm(
  formula = 
    HR_R_LM ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.HR_R_LM)
plot(model.HR_R_LM,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.HR_R_LM, type = "scatterplot")
plot(model.HR_R_LM, type = "scatterplot2")
plot(model.HR_R_LM, type = "qqplot")

model.HR_R_LM_interaction <-
  lmm(
  formula = 
    HR_R_LM ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.HR_R_LM_interaction)
plot(model.HR_R_LM_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.HR_R_LM_interaction, type = "scatterplot")
plot(model.HR_R_LM_interaction, type = "scatterplot2")
plot(model.HR_R_LM_interaction, type = "qqplot")
```

###HR_S_LM

```{r}

model.HR_S_LM<-
  lmm(
  formula = 
    HR_S_LM ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.HR_S_LM)
plot(model.HR_S_LM,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.HR_S_LM, type = "scatterplot")
plot(model.HR_S_LM, type = "scatterplot2")
plot(model.HR_S_LM, type = "qqplot")

model.HR_S_LM_interaction <-
  lmm(
  formula = 
    HR_S_LM ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.HR_S_LM_interaction)
plot(model.HR_S_LM_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.HR_S_LM_interaction, type = "scatterplot")
plot(model.HR_S_LM_interaction, type = "scatterplot2")
plot(model.HR_S_LM_interaction, type = "qqplot")
```

###MTT_Rest

```{r}

model.MTT_Rest<-
  lmm(
  formula = 
    MTT_Rest ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.MTT_Rest)
plot(model.MTT_Rest,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.MTT_Rest, type = "scatterplot")
plot(model.MTT_Rest, type = "scatterplot2")
plot(model.MTT_Rest, type = "qqplot")

model.MTT_Rest_interaction <-
  lmm(
  formula = 
    MTT_Rest ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.MTT_Rest_interaction)
plot(model.MTT_Rest_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.MTT_Rest_interaction, type = "scatterplot")
plot(model.MTT_Rest_interaction, type = "scatterplot2")
plot(model.MTT_Rest_interaction, type = "qqplot")


model.MTT_Rest_interaction2 <- #Controlled for IFN-1 signature
  lmm(
  formula = 
    MTT_Rest ~
    Timepoint+
    sex+
    Timepoint:treatment+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treatment,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)

plot(model.MTT_Rest_interaction2,
     col = "treatment",
     at = data.frame(sex = "Female", ifn_1_netto=median(pet_lung_data$ifn_1_netto, na.rm = T)),
     #facet = ~ treatment,
     ci = F,
     obs.alpha = 0.2)

plot(model.MTT_Rest_interaction2, type = "scatterplot")
plot(model.MTT_Rest_interaction2, type = "scatterplot2")
plot(model.MTT_Rest_interaction2, type = "qqplot")
```

###MTT_Stress

```{r}

model.MTT_Stress<-
  lmm(
  formula = 
    MTT_Stress ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.MTT_Stress)
plot(model.MTT_Stress,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.MTT_Stress, type = "scatterplot")
plot(model.MTT_Stress, type = "scatterplot2")
plot(model.MTT_Stress, type = "qqplot")

model.MTT_Stress_interaction <-
  lmm(
  formula = 
    MTT_Stress ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.MTT_Stress_interaction)
plot(model.MTT_Stress_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.MTT_Stress_interaction, type = "scatterplot")
plot(model.MTT_Stress_interaction, type = "scatterplot2")
plot(model.MTT_Stress_interaction, type = "qqplot")
```

###EDV_R

```{r}

model.EDV_R<-
  lmm(
  formula = 
    EDV_R ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.EDV_R)
plot(model.EDV_R,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.EDV_R, type = "scatterplot")
plot(model.EDV_R, type = "scatterplot2")
plot(model.EDV_R, type = "qqplot")

model.EDV_R_interaction <-
  lmm(
  formula = 
    EDV_R ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.EDV_R_interaction)
plot(model.EDV_R_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.EDV_R_interaction, type = "scatterplot")
plot(model.EDV_R_interaction, type = "scatterplot2")
plot(model.EDV_R_interaction, type = "qqplot")
```

###ESV_R
NOTE THIS MODEL IS OVERFITTED, See the residuals vs fitted plots.
```{r}

model.ESV_R<-
  lmm(
  formula = 
    ESV_R ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.ESV_R)
plot(model.ESV_R,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.ESV_R, type = "scatterplot")
plot(model.ESV_R, type = "scatterplot2")
plot(model.ESV_R, type = "qqplot")

model.ESV_R_interaction <-
  lmm(
  formula = 
    ESV_R ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.ESV_R_interaction)
plot(model.ESV_R_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.ESV_R_interaction, type = "scatterplot")
plot(model.ESV_R_interaction, type = "scatterplot2")
plot(model.ESV_R_interaction, type = "qqplot")
```

###SV_R

```{r}

model.SV_R<-
  lmm(
  formula = 
    SV_R ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.SV_R)
plot(model.SV_R,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.SV_R, type = "scatterplot")
plot(model.SV_R, type = "scatterplot2")
plot(model.SV_R, type = "qqplot")

model.SV_R_interaction <-
  lmm(
  formula = 
    SV_R ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.SV_R_interaction)
plot(model.SV_R_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.SV_R_interaction, type = "scatterplot")
plot(model.SV_R_interaction, type = "scatterplot2")
plot(model.SV_R_interaction, type = "qqplot")
```

###LVEF_R

```{r}

model.LVEF_R<-
  lmm(
  formula = 
    LVEF_R ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_R)
plot(model.LVEF_R,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_R, type = "scatterplot")
plot(model.LVEF_R, type = "scatterplot2")
plot(model.LVEF_R, type = "qqplot")

model.LVEF_R_interaction <-
  lmm(
  formula = 
    LVEF_R ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_R_interaction)
plot(model.LVEF_R_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_R_interaction, type = "scatterplot")
plot(model.LVEF_R_interaction, type = "scatterplot2")
plot(model.LVEF_R_interaction, type = "qqplot")
```

###EDV_S

```{r}

model.EDV_S<-
  lmm(
  formula = 
    EDV_S ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.EDV_S)
plot(model.EDV_S,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.EDV_S, type = "scatterplot")
plot(model.EDV_S, type = "scatterplot2")
plot(model.EDV_S, type = "qqplot")

model.EDV_S_interaction <-
  lmm(
  formula = 
    EDV_S ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.EDV_S_interaction)
plot(model.EDV_S_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.EDV_S_interaction, type = "scatterplot")
plot(model.EDV_S_interaction, type = "scatterplot2")
plot(model.EDV_S_interaction, type = "qqplot")
```

###ESV_S

```{r}

model.ESV_S<-
  lmm(
  formula = 
    ESV_S ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.ESV_S)
plot(model.ESV_S,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.ESV_S, type = "scatterplot")
plot(model.ESV_S, type = "scatterplot2")
plot(model.ESV_S, type = "qqplot")

model.ESV_S_interaction <-
  lmm(
  formula = 
    ESV_S ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.ESV_S_interaction)
plot(model.ESV_S_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.ESV_S_interaction, type = "scatterplot")
plot(model.ESV_S_interaction, type = "scatterplot2")
plot(model.ESV_S_interaction, type = "qqplot")
```

###SV_S

```{r}

model.SV_S<-
  lmm(
  formula = 
    SV_S ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.SV_S)
plot(model.SV_S,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.SV_S, type = "scatterplot")
plot(model.SV_S, type = "scatterplot2")
plot(model.SV_S, type = "qqplot")

model.SV_S_interaction <-
  lmm(
  formula = 
    SV_S ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.SV_S_interaction)
plot(model.SV_S_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.SV_S_interaction, type = "scatterplot")
plot(model.SV_S_interaction, type = "scatterplot2")
plot(model.SV_S_interaction, type = "qqplot")
```

###LVEF_S

```{r}

model.LVEF_S<-
  lmm(
  formula = 
    LVEF_S ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_S)
plot(model.LVEF_S,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_S, type = "scatterplot")
plot(model.LVEF_S, type = "scatterplot2")
plot(model.LVEF_S, type = "qqplot")

model.LVEF_S_interaction <-
  lmm(
  formula = 
    LVEF_S ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_S_interaction)
plot(model.LVEF_S_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_S_interaction, type = "scatterplot")
plot(model.LVEF_S_interaction, type = "scatterplot2")
plot(model.LVEF_S_interaction, type = "qqplot")
```

###LVEF_Reser

```{r}

model.LVEF_Reser<-
  lmm(
  formula = 
    LVEF_Reser ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_Reser)
plot(model.LVEF_Reser,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_Reser, type = "scatterplot")
plot(model.LVEF_Reser, type = "scatterplot2")
plot(model.LVEF_Reser, type = "qqplot")

model.LVEF_Reser_interaction <-
  lmm(
  formula = 
    LVEF_Reser ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.LVEF_Reser_interaction)
plot(model.LVEF_Reser_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.LVEF_Reser_interaction, type = "scatterplot")
plot(model.LVEF_Reser_interaction, type = "scatterplot2")
plot(model.LVEF_Reser_interaction, type = "qqplot")
```

###PBV_R

```{r}

model.PBV_R<-
  lmm(
  formula = 
    PBV_R ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.PBV_R)
plot(model.PBV_R,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.PBV_R, type = "scatterplot")
plot(model.PBV_R, type = "scatterplot2")
plot(model.PBV_R, type = "qqplot")

model.PBV_R_interaction <-
  lmm(
  formula = 
    PBV_R ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.PBV_R_interaction)
plot(model.PBV_R_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.PBV_R_interaction, type = "scatterplot")
plot(model.PBV_R_interaction, type = "scatterplot2")
plot(model.PBV_R_interaction, type = "qqplot")
```

###PBS_S

```{r}

model.PBS_S<-
  lmm(
  formula = 
    PBS_S ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.PBS_S)
plot(model.PBS_S,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.PBS_S, type = "scatterplot")
plot(model.PBS_S, type = "scatterplot2")
plot(model.PBS_S, type = "qqplot")

model.PBS_S_interaction <-
  lmm(
  formula = 
    PBS_S ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.PBS_S_interaction)
plot(model.PBS_S_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.PBS_S_interaction, type = "scatterplot")
plot(model.PBS_S_interaction, type = "scatterplot2")
plot(model.PBS_S_interaction, type = "qqplot")
```

###O2_vent_thresh

```{r}

model.O2_vent_thresh<-
  lmm(
  formula = 
    O2_vent_thresh ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.O2_vent_thresh)
plot(model.O2_vent_thresh,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.O2_vent_thresh, type = "scatterplot")
plot(model.O2_vent_thresh, type = "scatterplot2")
plot(model.O2_vent_thresh, type = "qqplot")

model.O2_vent_thresh_interaction <-
  lmm(
  formula = 
    O2_vent_thresh ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.O2_vent_thresh_interaction)
plot(model.O2_vent_thresh_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.O2_vent_thresh_interaction, type = "scatterplot")
plot(model.O2_vent_thresh_interaction, type = "scatterplot2")
plot(model.O2_vent_thresh_interaction, type = "qqplot")
```

###CO2_vent_thresh

```{r}

model.CO2_vent_thresh<-
  lmm(
  formula = 
    CO2_vent_tresh ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.CO2_vent_thresh)
plot(model.CO2_vent_thresh,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.CO2_vent_thresh, type = "scatterplot")
plot(model.CO2_vent_thresh, type = "scatterplot2")
plot(model.CO2_vent_thresh, type = "qqplot")

model.CO2_vent_thresh_interaction <-
  lmm(
  formula = 
    CO2_vent_tresh ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.CO2_vent_thresh_interaction)
plot(model.CO2_vent_thresh_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.CO2_vent_thresh_interaction, type = "scatterplot")
plot(model.CO2_vent_thresh_interaction, type = "scatterplot2")
plot(model.CO2_vent_thresh_interaction, type = "qqplot")
```

###vslope_vent_threshold

```{r}

model.vslope_vent_threshold<-
  lmm(
  formula = 
    vslope_vent_threshold ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.vslope_vent_threshold)
plot(model.vslope_vent_threshold,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.vslope_vent_threshold, type = "scatterplot")
plot(model.vslope_vent_threshold, type = "scatterplot2")
plot(model.vslope_vent_threshold, type = "qqplot")

model.vslope_vent_threshold_interaction <-
  lmm(
  formula = 
    vslope_vent_threshold ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.vslope_vent_threshold_interaction)
plot(model.vslope_vent_threshold_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.vslope_vent_threshold_interaction, type = "scatterplot")
plot(model.vslope_vent_threshold_interaction, type = "scatterplot2")
plot(model.vslope_vent_threshold_interaction, type = "qqplot")
```

###FSS

```{r}

model.FSS<-
  lmm(
  formula = 
    FSS ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.FSS)
plot(model.FSS,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.FSS, type = "scatterplot")
plot(model.FSS, type = "scatterplot2")
plot(model.FSS, type = "qqplot")

model.FSS_interaction <-
  lmm(
  formula = 
    FSS ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.FSS_interaction)
plot(model.FSS_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.FSS_interaction, type = "scatterplot")
plot(model.FSS_interaction, type = "scatterplot2")
plot(model.FSS_interaction, type = "qqplot")
```

###aerobic_capacity

```{r}

model.aerobic_capacity<-
  lmm(
  formula = 
    aerobic_capacity ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.aerobic_capacity)
plot(model.aerobic_capacity,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.aerobic_capacity, type = "scatterplot")
plot(model.aerobic_capacity, type = "scatterplot2")
plot(model.aerobic_capacity, type = "qqplot")

model.aerobic_capacity_interaction <-
  lmm(
  formula = 
    aerobic_capacity ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.aerobic_capacity_interaction)
plot(model.aerobic_capacity_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.aerobic_capacity_interaction, type = "scatterplot")
plot(model.aerobic_capacity_interaction, type = "scatterplot2")
plot(model.aerobic_capacity_interaction, type = "qqplot")
```

###vo_2_max

```{r}

model.vo_2_max<-
  lmm(
  formula = 
    vo_2_max ~ Timepoint + treat:Timepoint+sex,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.vo_2_max)
plot(model.vo_2_max,
     col = "treatment",
     at = data.frame(sex = "Female"),
     ci = F,
     obs.alpha = 0.2)

plot(model.vo_2_max, type = "scatterplot")
plot(model.vo_2_max, type = "scatterplot2")
plot(model.vo_2_max, type = "qqplot")

model.vo_2_max_interaction <-
  lmm(
  formula = 
    vo_2_max ~
    Timepoint+
    sex+
    Timepoint:treat+
    ifn_1_netto+
    ifn_1_netto:Timepoint+
    ifn_1_netto:Timepoint:treat,
  repetition = ~Timepoint|id,
  structure = "UN",
  data=pet_lung_data
)
summary(model.vo_2_max_interaction)
plot(model.vo_2_max_interaction,
     col = "treatment",
     at = data.frame(sex = "Female"),
     facet = ~ cut_interval(ifn_1_netto, 3),
     ci = F,
     obs.alpha = 0.2)

plot(model.vo_2_max_interaction, type = "scatterplot")
plot(model.vo_2_max_interaction, type = "scatterplot2")
plot(model.vo_2_max_interaction, type = "qqplot")
```

### For Loop

```{r eval = F}
list_main_models <- list()
list_interaction_models <- list()
list_outcomes<-list(
              "fev_1",
              "fev_1_pred",
              "fev_1_fvc_rå",
              "fev_fvc_pred",
              "tlv_rå",
              "tlv_pred",
              "rv_rå",
              "rv_pred",
              "dlc_oc_rå",
              "dlc_oc_pred",
              "va_rå",
              "va_pred",
              "kco_rå",
              "kco_pred",
              "HR_R_(LM)",
              "HR_S_(LM)",
              "MTT_Rest",
              "MTT_Stress",
              "EDV_R","ESV_R","SV_R","LVEF_R",
              "EDV_S","ESV_S","SV_S","LVEF_S",
              "LVEF_Reser",
              "PBV_R","PBS_S",
              "S/R ratio PBV",     
           #TODO Add lung parameters and PET parameters
              #weekly_exercise_sessions_baseline +
              #exercise_intensity_baseline +
              #exercise_duration_baseline +
              #"SLE_duration_months",
              #"SLEDAI_score",
              #"slicc_score",
              "FSS",
              "aerobic_capacity",
              "vo_2_max",
              "O2_vent_thresh",
              "CO2_vent_tresh",
              "vslope_vent_threshold",
              "duration_daily_MVPA_pla",
              "Energy_kJ_mean",
              "total_fat_percentage"
  )

for (var in list_outcomes){
  model_main <-
    lmm(
      formula = reformulate(
        "Timepoint + treat:Timepoint + sex",
        response = var
      ),
    repetition = ~Timepoint|id,
    structure = "UN",
    data=pet_lung_data
    )
  
  #plot(
  #  model_main, col = "treatment", 
  #   ci = F,
  #   obs.alpha = 0.2
  #)
  #plot(model_main, type = "scatterplot")
  #plot(model_main, type = "scatterplot2")
  #plot(model_main, type = "qqplot")
  #summary(model_main)
  
  model_main_list <- list(
     plot(
    model_main, col = "treatment", 
     ci = F,
     obs.alpha = 0.2
  ),
  plot(model_main, type = "scatterplot"),
  plot(model_main, type = "scatterplot2"),
  plot(model_main, type = "qqplot"),
  summary(model_main)
  )
  
  list_main_models[var]<-model_main_list
  
}


```

Let's test the
